---
title       : Slidify 
subtitle    : A Tutorial
author      : Gregorio Ambrosio
job         : Apr. 17 2018
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
logo        : goyologo.png # Graphic files will be in ~/myDeck/assets/img
biglogo     : goyologo.png
license     : by-nc-sa
assets      : {assets: ../../assets} # Add an assets directory
ext_widgets : {rCharts: [libraries/nvd3, libraries/leaflet, libraries/dygraphs]}
---

## What is Slidify

Slidify is a tool that makes it easy to create, customize and publish,
reproducible HTML5 slide decks using R Markdown.

Slidify helps create, customize and share, elegant, dynamic and interactive
HTML5 documents using R Markdown.

---

## Installation

Obviously you need a R environment. For that, install [R](https://www.r-project.org/) and [RStudio](https://www.rstudio.com/)

Slidify is not on CRAN and needs to be installed from github using the devtools package. I would recommend installing the dev version of the package.

```{r, eval=FALSE}
pkgs <- c("slidify", "slidifyLibraries", "rCharts")
devtools::install_github(pkgs, "ramnathv")
```

slidify.github.io recommends installing the `dev` version of the package

```{r, eval=FALSE}
install_github(pkgs, 'ramnathv', ref = 'dev')
```

Now you are ready to create your first slidify presentation.

--- 

## Create a new Deck

Each presentation is called a 'deck'. To create a new deck open RStudio, set
your working directory and use the `author` command.

```{r, eval=FALSE}
setwd("/path/to/")
require(slidify)
author("myDeck")
```

`/path/to/myDeck` is created.

Create a R Project from Existing Directory

```
File -> New Project -> Existing Directory -> /path/to/myDeck -> Create Project
```

A file called `myDeck.Rproj` will be created under `/path/to/myDeck`.

---

## Integration with Git ##

If git is installed, then the `author` command also initializes a git repository,
switchs to a `gh-pages` branch and commit all changes.

Before uploading your deck to your favourite Git cloud provider create
`.gitignore` to avoid version control for non essential files.

```{sh, eval=FALSE}
cd /path/to/myDeck
touch .gitignore
vim .gitignore
```

Add your ignored extensions

```{sh, eval=FALSE}
# RStudio files #
.Rproj.user
.Rhistory
.RData
.Ruserdata
# ...
```

---

## Upload the new repository (Bitbucket or GitHub)

Create an empty Repository, e.g. `myDeck` in BitBucket or GitHub. With an empty
repository a default branch called `master` won't be created. Then `push` the
local `myDeck` repository to the remote `myDeck` repo. Note that a new branch
called `gh-pages` has been created.

```sh
cd /path/to/myDeck
git add .
git commit -am "Initial commit"
git remote add origin_github https://github.com/username/myDeck.git
git remote add origin_bitbucket https://username@bitbucket.org/username/myDeck.git
git push -u origin[_github|bitbucket] --all
git push -u origin[_github|bitbucket] --tags
```

Now you can work with your new repository as usual

---

## Cloning your repo

To clone the repo on your machine take in account that you'll need to clone `gh-pages` branch

```shell-script
git clone -b gh-pages https://github.com/username/myDeck.git
```

or

```shell-script
git clone -b gh-page https://username@bitbucket.org/username/myDeck.git
```

---


## Tutorials

1. [Introduction](http://slidify.github.io/workshops/tutorials/01)
2. [Frameworks](http://slidify.github.io/workshops/tutorials/02)
3. [Layouts](http://slidify.github.io/workshops/tutorials/03)
4. [Widgets](http://slidify.github.io/workshops/tutorials/04)

--- .class #id

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- 

# Heading 1 #

## Heading 2 ##

### Heading 3 ###

#### Heading 4 ####

Body

 




