---
title       : Slidify 
subtitle    : Introductory Course
author      : Gregorio Ambrosio
job         : Apr. 17 2018
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
logo        : goyologo.png # Graphic files will be in ~/myDeck/assets/img
biglogo     : goyologo.png
license     : by-nc-sa
assets      : {assets: ../../assets} # Add an assets directory
ext_widgets : {rCharts: [libraries/nvd3, libraries/leaflet, libraries/dygraphs]}
---

## What is Slidify

Slidify is a tool that makes it easy to create, customize and publish, reproducible HTML5 slide decks using R Markdown.

Slidify helps create, customize and share, elegant, dynamic and interactive HTML5 documents using R Markdown.

---

## Installation

Obviously you need a R environment. For that, install [R](https://www.r-project.org/) and [RStudio](https://www.rstudio.com/)

Slidify is not on CRAN and needs to be installed from github using the devtools package. I would recommend installing the dev version of the package.

```{r, eval=FALSE}
pkgs <- c("slidify", "slidifyLibraries", "rCharts")
devtools::install_github(pkgs, "ramnathv")
```

slidify.github.io recommends installing the `dev` version of the package

```{r, eval=FALSE}
install_github(pkgs, 'ramnathv', ref = 'dev')
```

Now you are ready to create your first slidify presentation.

--- 

## Create a new Deck ##

Each presentation is called a 'deck'

Open RStudio

```
setwd("~/Git")

require(slidify)
author("myDeck") # It creates ~/Git/myDeck
```

Create a new Project from existing directory.

---

## Tutorials

1. [Introduction](http://slidify.github.io/workshops/tutorials/01)
2. [Frameworks](http://slidify.github.io/workshops/tutorials/02)
3. [Layouts](http://slidify.github.io/workshops/tutorials/03)
4. [Widgets](http://slidify.github.io/workshops/tutorials/04)

--- .class #id

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- 

# Heading 1 #

## Heading 2 ##

### Heading 3 ###

#### Heading 4 ####

Body

 




